### 2016-01-18 paper.tex
Add links to GitHub repo; resolves #20

The present task was to acquire a new experimental dataset for the lower
solidity RM2 turbine at sufficient Reynolds numbers to be relevant to full-scale
modeling. It was hypothesized that the parasitic losses from rotor blade support
struts could play an important role in overall turbine performance. Thus, the
parasitic torque from strut drag was measured without blades, then deliberately
and significantly increased in the physical model to provide data to help answer
that question. The velocity field in the near-wake of the turbine was then
measured to compare with measurements from a higher solidity rotor in the same
experimental setup \cite{Bachant2015-JoT}, and provide validation data for
numerical models that predict wake flows, which determine turbine--turbine
interaction and optimal spacing for turbine arrays. This dataset, along with the
code for processing and visualization, is publicly available
\cite{Bachant2015-RM2-data}.

@@

This data, along with the code for processing and visualization, is provided
openly via a Creative Commons license, and is available from
\cite{Bachant2015-RM2-data}. The authors hope that this can provide
opportunities for extensive validation of predictive tools for the complex
unsteady flow physics of cross-flow turbines.

>>>>

The present task was to acquire a new experimental dataset for the lower
solidity RM2 turbine at sufficient Reynolds numbers to be relevant to full-scale
modeling. It was hypothesized that the parasitic losses from rotor blade support
struts could play an important role in overall turbine performance. Thus, the
parasitic torque from strut drag was measured without blades, then deliberately
and significantly increased in the physical model to provide data to help answer
that question. The velocity field in the near-wake of the turbine was then
measured to compare with measurements from a higher solidity rotor in the same
experimental setup \cite{Bachant2015-JoT}, and provide validation data for
numerical models that predict wake flows, which determine turbine--turbine
interaction and optimal spacing for turbine arrays. This dataset, along with the
code for processing and visualization, is publicly available (licensed via
Creative Commons CC-BY for data and MIT license for code) as a Git repository on
GitHub (\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citeable
archive with a digital object identifier (DOI) \cite{Bachant2015-RM2-data}.

@@

This data, along with the code for processing and visualization, is provided
openly via a Creative Commons license (MIT license for code), and is available
as a Git repository from \url{http://github.com/UNH-CORE/RM2-tow-tank} or a
citeable archive \cite{Bachant2015-RM2-data}. The authors hope that this can
provide opportunities for extensive validation of predictive tools for the
complex unsteady flow physics of cross-flow turbines.
